j_play

### 2020-12-07 scripts/Final_project.Rmd
References section round 2

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}
library("papaja")
r_refs("r-references.bib")
library(here)
library(tidyverse)
library("readxl")
library(janitor)
library(esc)
library(dplyr)

@@

install.packages("GGally")
library(GGally)

@@

# References

RStudio Team (2020). RStudio: Integrated Development Environment for R.
  RStudio, PBC, Boston, MA URL http://www.rstudio.com/.

>>>>

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}
library("papaja")
r_refs("r-references.bib")
library(here)
library(tidyverse)
library("readxl")
library(janitor)
library(esc)
library(dplyr)
library(GGally)

@@

@@

\newpage
# References

@book{american2013diagnostic,
  title={Diagnostic and statistical manual of mental disorders (DSM-5{\textregistered})},
  author={American Psychiatric Association and others},
  year={2013},
  publisher={American Psychiatric Pub}
}

@article{ball1998big,
  title={Big policies/small world: An introduction to international perspectives in education policy},
  author={Ball, Stephen J},
  journal={Comparative education},
  volume={34},
  number={2},
  pages={119--130},
  year={1998},
  publisher={Taylor \& Francis}
}

@Manual{R-base,
  title = {R: A Language and Environment for Statistical Computing},
  author = {{R Core Team}},
  organization = {R Foundation for Statistical Computing},
  address = {Vienna, Austria},
  year = {2020},
  url = {https://www.R-project.org/},
}

@article{cohen2009school,
  title={School climate: Research, policy, practice, and teacher education},
  author={Cohen, Jonathan and McCabe, Libby and Michelli, Nicholas M and Pickeral, Terry},
  journal={Teachers college record},
  volume={111},
  number={1},
  pages={180--213},
  year={2009},
  publisher={Columbia}
}

citation("dplyr")

citation("esc")

citation("GGally")

@article{gu2018principals,
  title={How principals of successful schools enact education policy: Perceptions and accounts from senior and middle leaders},
  author={Gu, Qing and Sammons, Pam and Chen, Junjun},
  journal={Leadership and Policy in Schools},
  volume={17},
  number={3},
  pages={373--390},
  year={2018},
  publisher={Taylor \& Francis}
}

citation("here")

citation("janitor")

@article{kanevsky2013accelerating,
  title={Accelerating Gifted Students in Canada: Policies and Possibilities.},
  author={Kanevsky, Lannie S and Clelland, Debbie},
  journal={Canadian Journal of Education},
  volume={36},
  number={3},
  pages={229--271},
  year={2013},
  publisher={JSTOR}
}

@article{lambert2017public,
  title={Public education: Reflections on fifteen years of public policy},
  author={Lambert, Susan},
  journal={BC Studies: The British Columbian Quarterly},
  number={194},
  pages={163--173},
  year={2017}
}

@article{lo2019reenvisioning,
  title={Reenvisioning Gifted Education in British Columbia: A Qualitative Research Protocol of Policy Analysis in the Context of a Redesigned Curriculum},
  author={Lo, C Owen and Tan, Yuen Sze Michelle and Chrostowski, Megan and Hu, Shun-Fu and Chan, Diana and Sue, Deanna M and Wu, I-Chen and Li, Wei},
  journal={International Journal of Qualitative Methods},
  volume={18},
  pages={1609406918822233},
  year={2019},
  publisher={SAGE Publications Sage CA: Los Angeles, CA}
}

@article{luke2009model,
  title={A model for research-based state professional development policy},
  author={Luke, Allan and McArdle, Felicity},
  journal={Asia-Pacific Journal of Teacher Education},
  volume={37},
  number={3},
  pages={231--251},
  year={2009},
  publisher={Taylor \& Francis}
}

@article{michelmore2017gap,
  title={The gap within the gap: Using longitudinal data to understand income differences in educational outcomes},
  author={Michelmore, Katherine and Dynarski, Susan},
  journal={AERA Open},
  volume={3},
  number={1},
  pages={2332858417692958},
  year={2017},
  publisher={SAGE Publications Sage CA: Los Angeles, CA}
}

@Manual{R-papaja,
  author = {Frederik Aust and Marius Barth},
  title = {{papaja}: {Create} {APA} manuscripts with {R Markdown}},
  year = {2020},
  note = {R package version 0.1.0.9997},
  url = {https://github.com/crsh/papaja},
}

citation("readxl")

@article{swanson2007policy,
  title={Policy and practice: A case study of gifted education policy implementation},
  author={Swanson, Julie Dingle},
  journal={Journal for the Education of the Gifted},
  volume={31},
  number={2},
  pages={131--164},
  year={2007},
  publisher={SAGE Publications Sage CA: Los Angeles, CA}
}

citation("tidyverse")
